%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\usepackage[normalem]{ulem}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Nand Thaker} \\ \vspace{2pt}
    {\small \textit{Dual U.S. and Canadian citizen. Authorized to work in the U.S. and Canada without sponsorship.}} \\ \vspace{4pt}
    \small \raisebox{-0.1\height}\faPhone\ 437-983-6202 ~ 
    \href{mailto:thaker31@uwindsor.ca}{\raisebox{-0.2\height}\faEnvelope\ \underline{thaker31@uwindsor.ca}} ~ 
    \href{https://www.linkedin.com/in/nand-thaker-b919482aa/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} ~
    \href{https://github.com/nandth}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/nandth}}
    \vspace{-8pt}
\end{center}


%------RELEVANT COURSEWORK-------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL, Bash} \\
     \textbf{Developer Tools}{: GitHub Actions, Postman, GitHub, Docker} \\
     \textbf{Backend}{: FastAPI, Pydantic, Uvicorn, Node.js, Express.js, Docker, PostgreSQL, SQLAlchemy, Tenacity, SQLite} \\
     \textbf{Frontend}{: React, TailwindCSS, Vite, Framer Motion, WebGL, GLSL, OGL} \\
     \textbf{Testing}{: pytest, Jest, ESLint} \\
     \textbf{Systems}{: REST API Design, Rate Limiting, Streaming (SSE), Input Validation, Request Logging, Retry Strategies} \\
    }}
 \end{itemize}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Windsor}{Sep. 2024 -- Sep 2028}
      {Bachelor of Science, Computer Science, Specialization in Software Engineering }{Windsor, ON}
  \resumeSubHeadingListEnd


    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Selected Projects}
\resumeSubHeadingListStart

\resumeSubheading
  {\textbf{Cost-Aware LLM Router} $|$ {\mdseries\itshape Python (FastAPI, Pydantic, Uvicorn), React, Vite, TailwindCSS}}{}
  {Developer $|$ {\upshape \uline{\href{https://model-router-ai-five.vercel.app/}{LIVE}} \textbullet\ \uline{\href{https://github.com/nandth/model-router-ai}{GitHub}}}}{}
\resumeItemListStart
  \resumeItem{Built a full-stack LLM routing system with tiered model selection and prompt complexity scoring to route requests across cost and quality tiers.}
  \resumeItem{Implemented confidence-based escalation and fail-closed JSON parsing to prevent unsafe or malformed outputs from passing through.}
  \resumeItem{Added automated tests for routing logic, feature extraction, and parsing to cover core decision paths.}
  \resumeItem{Added per-IP rate limiting, input sanitization that preserves code formatting, and exponential backoff retries.}
  \resumeItem{Implemented SSE streaming and multiple API modes (standard, streaming, analysis-only) with structured telemetry in responses.}
\resumeItemListEnd
\resumeSubheading
  {\textbf{Broccolli URL Shortener (WIP)} $|$ {\mdseries\itshape React, Vite, TailwindCSS, Express, PostgreSQL}}{}
  {Developer $|$ {\upshape \uline{\href{https://github.com/notaarryan/broccolli-url-shortener}{GitHub}}}}{}
\resumeItemListStart
  \resumeItem{Building a full-stack URL shortener using React (Vite) and Express with a PostgreSQL data layer for URL storage and click analytics.}
  \resumeItem{Implemented deterministic hash-based short IDs using SHA-256 and Base62 to generate stable 7-character links.}
  \resumeItem{Developed a redirect service that resolves short codes, increments click counts, and performs HTTP redirects.}
  \resumeItem{Added resilient API handling with fallback logic for legacy endpoints and timeouts to improve reliability.}
  \resumeItem{Integrated framer-motion for result reveals and prefers-reduced-motion for accessibility.}
  \resumeItem{Implemented a WebGL shader background (OGL) to deliver a performant animated gradient experience.}
  \resumeItem{Implemented URL and slug input validation with inline guidance and client-side state handling for success and error flows.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-16pt}

%-----------PROJECTS-----------
\section{Additional Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Math Game} $|$ \emph{Java} $|$ {\upshape \uline{\href{https://github.com/nandth/kids-game-java}{GitHub}}}}{}
\resumeItemListStart
  \resumeItem{Designed and implemented a Java-based interactive quiz engine using Swing, applying core OOP principles including encapsulation, abstraction, modularity, and separation of concerns.}
  \resumeItem{Implemented Swing-based UI with CardLayout and event-driven state transitions using ActionListener patterns.}
  \resumeItem{Implemented four distinct game modes by defining a shared game-mode interface and overriding behavior per mode without duplicating UI or control logic.}
\resumeItemListEnd 
\vspace{-13pt}

\resumeProjectHeading
{\textbf{Macro Recorder} $|$ \emph{Python} $|$ {\upshape \uline{\href{https://github.com/nandth/macro-recorder}{GitHub}}}}{}
\resumeItemListStart
  \resumeItem{Built a desktop application in Python to record and replay mouse and keyboard movements.}
  \resumeItem{Designed a modular desktop UI using customtkinter, separating UI controls from macro execution logic.}
  \resumeItem{Saved the macros as human-readable JSON files for easy sharing.}
  \resumeItem{Implemented global input capture and deterministic playback for mouse movement, clicks, scrolling, and keyboard press/release events using pynput.}
\resumeItemListEnd 

\resumeSubHeadingListEnd
\vspace{-18pt}



%
%-----------PROGRAMMING SKILLS-----------





\end{document}
